---
title: "seismophobia_report"
author: "Trevor Kinsey, Dustin Andrews, Dustin Burnham, Junghoo Kim"
bibliography: seismophobia_refs.bib
date: "26/11/2020"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(reticulate)
```

## Summary
We will build a random forest classification model that will whether someone is afraid of earthquakes based on their demographic information. [I will put more information about the results here when I have them]

## Introduction

The damage that earthquakes cause can leave people without food, water, and shelter. Being prepared for an earthquake before it happens can make living through the immediate aftermath less traumatic (REFERENCE???). Having insurance that covers the damage caused by earthquakes can reduce the uncertainty and fear that the threat of earthquakes creates. People who are afraid of earthquakes represent a group of potential clients for companies selling earthquake preparedness products and insurance.

We aim to predict groups in the population are afraid of earthquakes and thus are target demographics for advertising. If a machine learning algorithm can identify these groups it enable companies to build a marketing strategy based on this information.

## Methods

## Data

The data for this analysis was downloaded from https://github.com/fivethirtyeight/data/tree/master/san-andreas. It is based on a survey conducted by ???????????????  in May 2015, of 1014 respondents in the US. 

The dataset contains:
 - demographic information (age, gender, household income, region), 
 - responses to questions relating to knowledge of and experience with earthquakes,
 - self-reported level of fear of earthquakes.




## Analysis

We used a random forest classifier and for the prediction, which in addition to predicting gives a measure of importance for each feature. We chose to use only the demographic variables as model features because they are available in census data without having to conduct another survey. The prediction target is the self-reported fear of earthquakes, which we converted from an ordinal variable to a binary variable called `target`. `target` = 1 includes the levels _"not at all worried"_ and _"not so worried"_, while `target` = 1 includes _"somewhat worried"_, _"very worried"_, and _"extremely worried"_.  

The R [@R] and Python [@van1995python] programming languages and the following Python packages were used for this project: pandas [@reback2020pandas], sklearn [@scikit-learn], tidyverse [@tidyverse], knitr [@knitr] and docopt [XXXXXXXXXX@docopt].
The code used to perform the analysis and create this report can be found at: https://github.com/UBC-MDS/seismophobia


## Results

As you can see, we need to add information here


```{r}

```



## References